---
title: "brandkit report"
author: "Your Name"
format:
  html:
    theme:
      light: [brand, brandkit.scss]
      dark: [brand, brandkit.scss]
    toc: true
---

::: {.brand-logo-container}
{{< brand logo medium >}}
:::

```{r}
#| label: setup
#| include: false
library(brandkit)
library(ggplot2)
library(plotly)
brand_quarto_setup()  # or brand_quarto_setup("dark") for dark-only docs
```

## Overview

This document inherits all styling from `_brand.yml` automatically.
Quarto handles the document theme; brandkit handles ggplot2 and plotly.

Use the toggle in the navbar to switch between light and dark mode.
Note: plots are rendered once at build time, so they match whichever
mode you pass to `brand_quarto_setup()`.

## Static ggplot2

```{r}
#| label: scatter
#| fig-cap: "Auto-themed — no theme_brand() needed"
ggplot(iris, aes(Sepal.Length, Sepal.Width, color = Species)) +
  geom_point(size = 3) +
  labs(title = "Iris Measurements")
```

## Interactive Plotly

```{r}
#| label: plotly-scatter
p <- ggplot(mtcars, aes(mpg, wt, color = factor(cyl))) +
  geom_point(size = 3) +
  labs(title = "MPG vs Weight", color = "Cylinders")

brand_plotly(p, tooltip = c("x", "y", "colour"))
```

## Plotly with Sequential Palette

```{r}
#| label: plotly-heatmap
p <- ggplot(faithfuld, aes(waiting, eruptions, fill = density)) +
  geom_tile() +
  scale_fill_brand_c(type = "warm") +
  labs(title = "Old Faithful Eruptions")

brand_plotly(p)
```

## Static Heatmap

```{r}
#| label: heatmap
#| fig-cap: "Warm sequential palette from brand colours"
ggplot(faithfuld, aes(waiting, eruptions, fill = density)) +
  geom_tile() +
  scale_fill_brand_c(type = "cool") +
  labs(title = "Old Faithful — Cool Palette")
```

## Brand Colours

```{r}
#| label: colours
str(brand_colors())
```
