---
title: "Air Quality in New York"
subtitle: "A polished starting point for branded Typst PDFs"
author: "Your Name"
date: today
format:
  brandkit-typst:
    toc: false
---

```{r}
#| label: setup
#| include: false
library(brandkit)
library(ggplot2)
brand_quarto_setup()

# Sample data - replace with your own. airquality is built into R: daily
# readings in New York, May to September 1973.
aq <- airquality
aq$Month <- factor(month.name[aq$Month], levels = month.name[5:9])
```

## Overview

This report was scaffolded by `create_brand_quarto_pdf()`. It renders to
PDF through Quarto's Typst engine using the `brandkit-typst` format
defined in `_extensions/brandkit/`. That extension layers a branded
title page (with logo), coloured headings, and a coloured footer rule
on top of Quarto's default Typst article template — on top of the
colour and font theming Quarto's own `_brand.yml` integration already
applies automatically.

Because a PDF has no light/dark toggle, plots are baked in at render
time using whichever mode you pass to `brand_quarto_setup()`.

## Branded Plot

```{r}
#| label: scatter
#| fig-cap: "Auto-themed via theme_brand() — no manual styling needed"
ggplot(aq, aes(Temp, Ozone, color = Month)) +
  geom_point(size = 3, na.rm = TRUE) +
  labs(x = "Temperature (°F)", y = "Ozone (ppb)", color = NULL)
```

## Branded Table

Monthly means: temperature in °F, ozone in ppb, wind in mph.

```{r}
#| label: table
monthly <- aggregate(cbind(Temp, Ozone, Wind) ~ Month, aq, mean,
                     na.rm = TRUE, na.action = na.pass)
knitr::kable(monthly, digits = 1)
```

## Brand Palette

```{r}
#| label: palette
#| fig-cap: "Discrete brand palette"
#| fig-height: 2
cols <- brand_pal_discrete()
barplot(rep(1, length(cols)), col = cols, border = NA, axes = FALSE)
```

## Next Steps

- Edit the YAML title block above for your own report.
- Add sections, tables, and ggplot2 plots as needed — they inherit
  brand colours and fonts automatically.
- Customise `_extensions/brandkit/typst-template.typ` for further
  layout changes (margins, title page, footer).
