---
title: "Summer Air Quality in New York"
subtitle: "Landscape, three columns, all inferred from _brand.yml"
author: "Your Name"
date: today
poster-footer: "Department of Everything | you@example.org | example.org/project"
format:
  brandkit-poster-typst:
    columns: 3
fig-width: 9
fig-height: 5.5
fig-dpi: 300
# A poster shows findings, not source. The one code listing below is a
# plain ```r fence, written out deliberately to show the brand's code
# styling - the chunks that draw the figures stay hidden.
execute:
  echo: false
---

```{r}
#| label: setup
#| include: false
library(brandkit)
library(ggplot2)
brand_quarto_setup()

# Plots fill the column they land in, so a figure drawn at 9in is
# enlarged to roughly 13in on A0 - which shrinks its labels relative to
# the poster's body copy. Raising the ggplot base size compensates, so
# axis text lands near the body text size instead of well under it.
theme_set(theme_brand(base_size = 22))

# Sample data - replace with your own. airquality is built into R: daily
# readings in New York, May to September 1973.
aq <- airquality
aq$Month <- factor(month.name[aq$Month], levels = month.name[5:9])
```

## Background {.plain}

Everything on this sheet - the colours, the fonts, the soft corner
ornaments, the card panels, the footer band - is inferred from
`_brand.yml`. Nothing here names a colour or a typeface.

The data are R's built-in `airquality`: daily ozone, solar radiation,
wind and temperature readings from New York, May to September 1973.

This section is marked `{.plain}`, so it runs free in the column instead
of sitting in a card: useful for a lead-in that should read as part of
the poster rather than as one of its findings.

## Methods

Write ordinary Markdown. Each `##` heading, and everything under it,
becomes a card. Cards never split across a column - one that does not
fit is moved to the next column whole, which is why a column sometimes
stops short of the bottom of the sheet.

Inline code such as `theme_brand()` and fenced blocks are styled from
the brand exactly as they are in the report formats:

```r
p <- ggplot(airquality, aes(Temp, Ozone, colour = factor(Month))) +
  geom_point(size = 4)
```

Chunks are hidden here via `execute: echo: false`, because a poster
shows findings rather than source. Drop that and the code appears,
styled the same way.

## Results

```{r}
#| label: scatter
#| fig-cap: "Auto-themed via theme_brand() - no manual styling"
#| fig-height: 4.5
#| out-width: "100%"
ggplot(aq, aes(Temp, Ozone, colour = Month)) +
  geom_point(size = 4, na.rm = TRUE) +
  labs(x = "Temperature (°F)", y = "Ozone (ppb)", colour = NULL)
```

Figures fill the column they land in, so their aspect ratio is what
`fig-width` and `fig-height` really control. Set `fig-height` per chunk
to decide how much of the column each one claims.

## Distributions

```{r}
#| label: box
#| fig-cap: "Ozone by month"
#| fig-height: 4
#| out-width: "100%"
ggplot(aq, aes(Month, Ozone, fill = Month)) +
  geom_boxplot(alpha = 0.85, show.legend = FALSE, na.rm = TRUE) +
  labs(x = NULL, y = "Ozone (ppb)")
```

Discrete scales come from the brand palette by default, so a second
figure agrees with the first without being told to.

## Key Numbers

```{r}
#| label: table
monthly <- aggregate(cbind(Temp, Ozone, Wind) ~ Month, aq, mean,
                     na.rm = TRUE, na.action = na.pass)
knitr::kable(monthly, digits = 1)
```

Monthly means in °F, ppb and mph, ruled and striped like the report
formats' tables.

## Brand Palette

```{r}
#| label: palette
#| fig-cap: "Discrete brand palette"
#| fig-height: 1.1
cols <- brand_pal_discrete()
# Base graphics keep a five-line default margin, which at this figure
# height leaves no plotting region at all ("figure margins too large").
par(mar = c(0, 0, 0, 0))
barplot(rep(1, length(cols)), col = cols, border = NA, axes = FALSE)
```

Base graphics work too - the palette helpers are plain colour vectors.

## Conclusions

- Ozone climbs with temperature; July and August are the worst months.
- A poster is a fixed sheet: overflow spills onto a second page.
- Re-run `create_brand_quarto_poster(paper = "a1", columns = 4)` to
  retarget the sheet.
