---
title: "Air Quality in New York"
subtitle: "A print-friendly starting point for branded PDFs"
author: "Your Name"
date: today
format:
  brandkit-print-typst:
    toc: false
---

```{r}
#| label: setup
#| include: false
library(brandkit)
library(ggplot2)
brand_quarto_setup()

# Sample data - replace with your own. airquality is built into R: daily
# readings in New York, May to September 1973.
aq <- airquality
aq$Month <- factor(month.name[aq$Month], levels = month.name[5:9])
```

## Overview

This report was scaffolded by `create_brand_quarto_print_pdf()`. It
renders to PDF through Quarto's Typst engine using the
`brandkit-print-typst` format in the project's `_extensions/brandkit-print/`
directory, which adds a plain title block with the logo, coloured headings
and a coloured footer rule (from page two: the title page has none) on top
of the colours and fonts Quarto's own `_brand.yml` integration already
applies.

The page is framed by a pair of soft corner ornaments on the first page,
drawn in the brand's colours at a low opacity, instead of a solid title
panel. Nothing bleeds off the page and very little ink is laid down, which
is what makes it the format for printing on an ordinary printer. For the
full-bleed striped banner, see `create_brand_quarto_pdf()`; both formats
can live in one project, so switch by changing the `format:` key at the top
of this file.

Because a PDF has no light/dark toggle, plots are baked in at render
time using whichever mode you pass to `brand_quarto_setup()`.

## Branded Plot

```{r}
#| label: scatter
#| fig-cap: "Auto-themed via theme_brand() — no manual styling needed"
ggplot(aq, aes(Temp, Ozone, color = Month)) +
  geom_point(size = 3, na.rm = TRUE) +
  labs(x = "Temperature (°F)", y = "Ozone (ppb)", color = NULL)
```

## Branded Table

Monthly means: temperature in °F, ozone in ppb, wind in mph.

```{r}
#| label: table
monthly <- aggregate(cbind(Temp, Ozone, Wind) ~ Month, aq, mean,
                     na.rm = TRUE, na.action = na.pass)
knitr::kable(monthly, digits = 1)
```

## Brand Palette

```{r}
#| label: palette
#| fig-cap: "Discrete brand palette"
#| fig-height: 2
cols <- brand_pal_discrete()
barplot(rep(1, length(cols)), col = cols, border = NA, axes = FALSE)
```

## Next Steps

- Edit the YAML title block above for your own report.
- Add sections, tables, and ggplot2 plots as needed — they inherit
  brand colours and fonts automatically.
- Customise `_extensions/brandkit-print/typst-template.typ` for further
  layout changes (margins, footer), or `page.typ` for the title block and
  the ornaments.
