---
title: "Air Quality in New York"
subtitle: "A polished starting point for branded HTML reports"
author: "Your Name"
date: today
format:
  html:
    title-block-style: none
    # The nested light:/dark: form is what gives the reader a working
    # light/dark toggle: Quarto emits a Bootstrap stylesheet per mode and
    # the toggle swaps between them. The flat `theme: [brand, drift.scss]`
    # form looks equivalent and still shows a toggle, but only the syntax
    # highlighting actually switches — the Bootstrap layer stays light.
    # Both lists are identical; _brand.yml's own color:/color-dark: entries
    # are what differ per mode.
    theme:
      light: [brand, drift.scss]
      dark: [brand, drift.scss]
    include-after-body: _ornaments.html
    toc: false
---

::: {.brand-masthead}
{{< brand logo medium >}}

::: {.brand-masthead-title}
{{< meta title >}}
:::

::: {.brand-masthead-subtitle}
{{< meta subtitle >}}
:::

::: {.brand-masthead-meta}
{{< meta author >}} · {{< meta date >}}
:::
:::

```{r}
#| label: setup
#| include: false
library(brandkit)
library(ggplot2)
library(plotly)
# adaptive = TRUE draws every plot in both colour modes, so the page's
# light/dark toggle switches the plots too.
brand_quarto_setup(adaptive = TRUE)

# Sample data - replace with your own. airquality is built into R: daily
# readings in New York, May to September 1973.
aq <- airquality
aq$Month <- factor(month.name[aq$Month], levels = month.name[5:9])
```

## Overview

This report was scaffolded by `create_brand_quarto_html()`. It inherits
all styling from `_brand.yml` automatically — Quarto handles the
document theme, brandkit handles ggplot2 and plotly. `drift.scss` is the
look (the plain title, the corner ornaments, the tables) and
`_ornaments.html` the ornaments themselves; edit either to adapt it.

## Branded Plot

```{r}
#| label: scatter
#| fig-cap: "Auto-themed via theme_brand() — no manual styling needed"
p <- ggplot(aq, aes(Temp, Ozone, color = Month)) +
  geom_point(size = 3, na.rm = TRUE) +
  labs(x = "Temperature (°F)", y = "Ozone (ppb)", color = NULL)
p
```

## Interactive Version

The same plot, made interactive with one extra function call:

```{r}
#| label: plotly-scatter
brand_plotly(p, tooltip = c("x", "y", "colour"))
```

## Branded Table

Monthly means: temperature in °F, ozone in ppb, wind in mph.

```{r}
#| label: table
monthly <- aggregate(cbind(Temp, Ozone, Wind) ~ Month, aq, mean,
                     na.rm = TRUE, na.action = na.pass)
knitr::kable(monthly, digits = 1)
```

## Brand Palette

```{r}
#| label: palette
#| fig-cap: "Discrete brand palette"
#| fig-height: 2
cols <- brand_pal_discrete()
barplot(rep(1, length(cols)), col = cols, border = NA, axes = FALSE)
```

::: {.brand-footer}
{{< meta title >}}

Made with [brandkit](https://github.com/LukasWillocx/brandkit)
:::
