---
title: "Air Quality in New York"
subtitle: "A polished starting point for branded revealjs slides"
author: "Your Name"
date: today
format:
  revealjs:
    theme: [brand, drift.scss]
    include-after-body: _ornaments.html
    slide-number: true
    transition: fade
    logo: medium
    footer: "{{< meta title >}}"
---

```{r}
#| label: setup
#| include: false
library(brandkit)
library(ggplot2)
library(plotly)
brand_quarto_setup()

# Sample data - replace with your own. airquality is built into R: daily
# readings in New York, May to September 1973.
aq <- airquality
aq$Month <- factor(month.name[aq$Month], levels = month.name[5:9])
```

## Overview

This deck was scaffolded by `create_brand_quarto_slides()`. Colours,
fonts, and styling come from `_brand.yml`; all ggplot2 and plotly
output is auto-themed. `drift.scss` is the look and `_ornaments.html`
the corner ornaments; edit either to adapt it.

## Branded Plot

```{r}
#| label: scatter
#| fig-width: 8
#| fig-height: 4
p <- ggplot(aq, aes(Temp, Ozone, color = Month)) +
  geom_point(size = 3, na.rm = TRUE) +
  labs(x = "Temperature (°F)", y = "Ozone (ppb)", color = NULL)
p
```

## Interactive Version

The same plot, made interactive with one extra function call:

```{r}
#| label: plotly
brand_plotly(p, tooltip = c("x", "y", "colour"), width = 1000, height = 600)
```

## Brand Palette

```{r}
#| label: palette
#| fig-width: 8
#| fig-height: 3
cols <- brand_pal_discrete()
barplot(rep(1, length(cols)), col = cols, border = NA, axes = FALSE,
        main = "Brand discrete palette")
```

## Dark Mode Slides

Set `brand-mode: dark` in the YAML header to render
the entire deck using your dark palette:

```yaml
format:
  revealjs:
    brand-mode: dark
```

And update the setup chunk:

```r
brand_quarto_setup("dark")
```
