---
title: "Brand Report"
subtitle: "A polished starting point for branded revealjs slides"
author: "Your Name"
date: today
title-slide-attributes:
  data-background-color: "__BRANDKIT_TITLE_BG__"
format:
  revealjs:
    theme: [brand, brandkit.scss]
    slide-number: true
    transition: fade
    logo: medium
    footer: "{{< meta title >}}"
---

```{r}
#| label: setup
#| include: false
library(brandkit)
library(ggplot2)
library(plotly)
brand_quarto_setup()
```

## Overview

This deck was scaffolded by `create_brand_quarto_slides()`. Colours,
fonts, and styling come from `_brand.yml`; all ggplot2 and plotly
output is auto-themed.

## Branded Plot

```{r}
#| label: scatter
#| fig-width: 8
#| fig-height: 4
p <- ggplot(mtcars, aes(mpg, wt, color = factor(cyl))) +
  geom_point(size = 3) +
  labs(title = "MPG vs Weight", color = "Cylinders")
p
```

## Interactive Version

The same plot, made interactive with one extra function call:

```{r}
#| label: plotly
brand_plotly(p, tooltip = c("x", "y", "colour"), width = 1000, height = 600)
```

## Brand Palette

```{r}
#| label: palette
#| fig-width: 8
#| fig-height: 3
cols <- brand_pal_discrete()
barplot(rep(1, length(cols)), col = cols, border = NA, axes = FALSE,
        main = "Brand discrete palette")
```

## Dark Mode Slides

Set `brand-mode: dark` in the YAML header to render
the entire deck using your dark palette:

```yaml
format:
  revealjs:
    brand-mode: dark
```

And update the setup chunk:

```r
brand_quarto_setup("dark")
```
